



## 1.)  Code for reading in the dataset and/or processing the data
```{r echo=TRUE}
library("sqldf")

MyData <- read.csv(file="activity.csv", header=TRUE, sep=",")

```

## 2.)Histogram of the total number of steps taken each day
```{r echo=TRUE}
library("sqldf")

temp <- sqldf("Select date, sum(steps) From MyData group by date")
temp$`sum(steps)` <- as.numeric(temp$`sum(steps)`)

hist(temp$`sum(steps)`, main = "Histogram of the total number of steps taken each day", xlab = "Steps" )
```

## 3.) Mean and median number of steps taken each day
```{r echo=TRUE}
myFun <- function(x) { c(mean = mean(x), median = median(x))}

tapply(MyData$steps,MyData$date , myFun)

```


## 4.) Time series plot of the average number of steps taken
```{r echo=TRUE}
library("sqldf")

temp3 <- sqldf("Select date, Avg(steps) From MyData group by date")
colnames(temp3)[2] <- "Avg_Steps"

temp3$date <- as.Date(temp3$date, "%Y-%m-%d")
plot(Avg_Steps ~ date, temp3, type = "l")

```


##  5.) The 5-minute interval that, on average, contains the maximum number of steps
```{r echo=TRUE}
library("sqldf")

temp4 <- sqldf("Select interval, Avg(steps) From MyData group by interval")
colnames(temp4)[2] <- "Avg_Steps"
sqldf("Select interval, Avg_Steps From temp4 where Avg_Steps = ( select Max(Avg_Steps) From temp4)")
```

##  6.) Code to describe and show a strategy for imputing missing data

    6.1 total number of missing values in the dataset (i.e. the total number of rows with NAs)
    
```{r echo=TRUE}

sqldf("Select count(interval) From MyData where steps is null ")

```

   6.2 filling in all of the missing values in the dataset with mean for that 5-minute interval.

```{r echo=TRUE}
library("sqldf")
library("dplyr")

MyData2 <- sqldf("Select MyData.*, temp4.Avg_Steps From MyData, temp4 where MyData.interval = temp4.interval  ")

MyData2 <- mutate( MyData2 , steps =  ifelse( is.na(steps) ,Avg_Steps, steps  )  )
MyData2 <- sqldf(" Select  steps , date, interval From  MyData2 "  )
head(MyData2)

```

##  7.) Histogram of the total number of steps taken each day after missing values are imputed
```{r echo=TRUE}
library("sqldf")

temp5 <- sqldf("Select date, sum(steps) From MyData2 group by date")
temp5$`sum(steps)` <- as.numeric(temp5$`sum(steps)`)
hist(temp5$`sum(steps)`, main = "Histogram of the total number of steps taken each day", xlab = "Steps")
```

##  8.)Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r echo=TRUE}

library("sqldf")
library("dplyr")

par(mfrow=c(1,2)) 
temp6 <- mutate( MyData2 , WeekDay =  weekdays( as.Date( date))  )

temp7 <- sqldf("Select interval, Avg(steps) From temp6 Where WeekDay in ( 'Monday','Tuesday' ,'Wednesday', 'Thursday','Friday')  group by interval")
colnames(temp7)[2] <- "Steps"
plot(temp7, main='weekdays',type = "l" )

temp8 <- sqldf("Select interval, Avg(steps) From temp6 Where WeekDay in ( 'Saturday', 'Sunday')  group by interval")
colnames(temp8)[2] <- "Steps"
plot(temp8, main='weekends',type = "l" )

```






